Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-05-02 Ben_Manuscripts/Outlines/Paper1_Outline.tex
edits

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{geometry}
\geometry{legalpaper, margin=1in}
\usepackage{amsmath} % or simply amstext
\newcommand{\angstrom}{\textup{\AA}}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
%MRS: we probably will want to add in Glaser's student (and possibly glaser) for their work on the X-ray simulations.
%MRS: also possibly Xunda if we end up using X-ray diffraction images of theirs that are not published.
\begin{document}
	\bibliographystyle{ieeetr}
	\graphicspath{{./figures/}}
	\maketitle
	\section{Introduction}
	Nanostructured membrane materials have become increasingly popular for aqueous separations applications because they offer the ability to control membrane architecture at the atomic scale allowing design of solute-specific separation membranes.
	\begin{itemize}
		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
		\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
		\item Designing RO membranes to achieve targeted separations of specific solutes is nearly impossible due to the separation (hypothesized to be) controlled by fluctuating polymer voids
		\item RO has difficulty separating neutral organics because they tend to dissolve in polymer matrix
		\item Many current RO membranes degrade in typical chlorine filled municipal water supplies (debating this point because there aren't any studies of LLC membrane fouling resistance)
                  %MRS: Doug should have information on the chemistry here and how resistant they might be.
		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
		\item Targeted separations can be accomplished by tuning the molecular building blocks which form these materials
		\item Entirely different mechanisms govern the separation processes in various nanostructured materials which can inspire novel separation techniques
	\end{itemize}

@@

	A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines to reduce the chemical space for design of monomers used to create separation-specific membranes.
	\begin{itemize}
                \item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effective water desalination and small organic separations. Rejection studies show that this membrane can not do desalination yet
%MRS: ^^^nice way to turn a weakness of the materials class into an opportunity to improve them requring research! 
		\item Colh phase studies currently limited to one monomer
                \item Optimization efforts performed through trial and error over the past 20 years
                \item Macroscopic models are the only source of predictive modeling and existing theories do not adequately describe transport at these length scales
                \begin{itemize}
                        \item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
                          %MRS: vvv this point below should be made more specific.  Ionic gradient at the end?  Donnan exclusion?
                        \item Does concentration of ions in the pore repel incoming ions?
                        \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection?
                         %MRS: vvv can you be a bit more specific about ``transport barriers?''
                        \item Is water structured inside the pores leading to transport barriers?
                          %MRS: vvv maybe put this higher, since the other bullet points above are dependent on this.  Also, this point conflacts understanding the structure, and then modifying it, which are sort of two steps.
			\item What does the microscopic pore structure look like and how can we relate that to monomer design and transport?
		\end{itemize}
		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
		\item We can use molecular dynamics simulations to enhance our understanding 
	\end{itemize}

	A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, 
%MRS: a molecular model can't really confirm or deny, because of the approximations.  provide evidence to support or call into question previous conclusions.
will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
	\begin{itemize}
		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
		\begin{itemize}
			\item This could change how one thinks about molecules diffusing through membrane
			\item Could also be a difference between lyotropic and thermotropic phases
		\end{itemize}
		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
		\begin{itemize}
			\item How do the monomer head groups pack together? Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
			\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation. 
			\item Substituted benzene preferred stacking mode? Learning more about this   	
			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer 
		\end{itemize}
		\item It is possible there is more than one metastable states associated with this LLC system
		\begin{itemize}
			\item Which phase is consistent with experiment?
			\item Can both phases be created experimentally?
			\item How will each state affect transport?
		\end{itemize}
	\end{itemize}

	We must show that the developed molecular model is consistent with physical observations so that we can trust conclusions drawn about structural features characteristic of the system.
	\begin{itemize}
          %MRS: ``careful'': better to show, not tell that it is careful.
		\item This paper will illustrate the development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
		\item We are primarily interested in reproducing the conclusions about structure which have been made from XRD experiments and ionic conductivity measurements.    
                  %MRS: algorithm not really the main finding.
		  %BJC: so don't mention it here then? maybe save it for the methods
		\item We examined crosslinking mechanism and understand its influence on membrane structure
                  %MRS: the fact that we can is not that much interest, rather that we do.  Restate along lines of ``we havecompared simulated x-ray diffraction to experiment''
		\item We can simulate x ray diffraction patterns based on atomic coordinates in order to compare major features present in the 2D patterns
		\item We can predict ionic conductivity using two agreeing methods -- Collective diffusion and nernst einstein
	\end{itemize}

@@

	An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
	\begin{itemize}
		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
		\item Result not global minimum but close enough for structure building
		\item Antechamber used for atomtyping with gaff forcefield
		\item Used Openeye Quacpac molcharge.py to assign charges %MRS: explain reason for 2 charge steps.
		\item Anneal again 
		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
		\item Manual modifications to the structure were made to create specific geometries for xray diffraction experiments
	\end{itemize}

	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for a more efficient way to build the system. 
	\begin{itemize}
		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
		\item Attempts with Colh system not fruitful  
		\begin{itemize}
			\item Packed monomers into box
			\item Simulated for ~100 ns with no progress shown towards self assembly
		\end{itemize}  
		\item Wrote code to assemble monomers into Colh configuration close to what is expected 
		\item Equilibration simulations allow structure to relax into expected configuration 
	\end{itemize}

@@

	\begin{figure}

	\includegraphics{placeholder.png}
		\caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
		\label{fig:initial}
	\end{figure}

@@

	An equilibration scheme with position restraints placed on benzene rings prevents unrealistic jumps during early equilibration steps.
	\begin{itemize}
		\item Equilibration scheme:
		\begin{itemize}
			\item Apply position restraints to monomer head groups during energy minimization 
			\item Leave position restraints on for nvt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
			\item Gradually reduce force constants from 1000000 (by square root every 50 ps) until they are completely off
			\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate 
		\end{itemize}
	\end{itemize}

@@

	% Ionic conductivity here probably
	The Nernst Einstein relation and the Collective Diffusion model were both applied to the system in order to estimate ionic conductivity.
		\item There are a few ways to estimate ionic conductivity as seen in literature. We prefer a method which can extract an estimate based purely on an equilibrium trajectory (reference to computational electrophysiology) 
                \item We must also be sure that our analysis of results is consistent with the method used for experimental evaluation (i.e. AC impedance spectroscopy)
                \item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system. %BJC: worth getting into? Could also just say 
		% that we expect our calculated value to be higher since ours is perfectly aligned relative to the real system.
                \item Two methods used to for prediction
                %BJC: probably belongs in methods:
                \item Nernst Einstein Relation:
                \begin{itemize}
                        \item Widely used equation for estimating ionic conductivity
                        \item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
                        \item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
                        \item Concentration is concentration of ions in the whole membrane, not just channels
                \end{itemize}
                \item Collective Diffusion:  %BJC: will have a very topical explanation followed by a reference to the paper from which I got the method
                \begin{itemize}
                        \item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
                        \item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
                        \item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
                        \item A similar model has been derived and validate to predict water permeability using equilibrium simulations
                        \item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores. One would expect single channel IC to be much larger than the bulk membrane
                \end{itemize}
        \end{itemize}

@@

	To understand the composition of the monomer layers, we ran simulations created with 4 - 8 monomers per layer 
	\begin{itemize}
		\item All configurations were stable for at least a short time %BJC: I am going to run out these simulations further and will have more to say
                \item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Fig~\ref{table:p2p})
        \end{itemize}

        The initial distance between layers is a key determining factor of the equilibrium configuration.
	\begin{itemize}
                \item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. 
                \item A characteristic of all systems simulated in this way, is a defined, cylindrical and open pore structure. Benzene rings arrange in a helical conformation after equil. Membrane about 8 nm thick (Fig ~\ref{fig:phaseA}) % BJC: Still trying to prove that layered is trying to go towards a helical conformation. Also, maybe include thickness in the table?
                \item This will be called phase A for simplicity  
	        Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
        	\begin{itemize}
                	\item This will be called phase B (Fig~\ref{fig:phaseB})
                	\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution 
                	\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the starting configuration
                	\item The phase is also present when phase A is heated close to its isotropic transition point
                	\item There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
                	\begin{itemize}
                        	\item Phase B has a closed pore, while phase A is open. This will impact transport mechanisms
                        	\item Phase B membranes are thicker
                        	\item Consequently, the pore spacing is smaller
                	\end{itemize}
                \item We have at least two metastable states
        \end{itemize}

	We varied the relative interlayer orientation between sandwiched and parallel-displaced based on our knowledge of the stability of these two pi-stacking modes.
        \begin{itemize}
		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a clear relation between the parallel displaced and sandwiched configuration %BJC: A figure would probably be good here
		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
		\item Both configurations are stable for 100's of nanoseconds
		\item Xray diffraction of the sandwiched configuration after equilibration shows the spots. This indicates that there is a shift towards the offset configuration.
	\end{itemize}

@@

	A summary of all experiments and relevant structural parameters are presented in table ~\ref{fig:p2p}

	\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{placeholder.png}
	\caption{As temperature is increased, Phase A transitions to Phase B, as indicated by the shown order parameter. An order parameter of 1 indicates perfect ordering, while 0 indicates disorder~\label{fig:transition}}
	\end{figure}

	\begin{table}
	\centering
	\begin{tabular}{|c|c|}
	\hline
	table & here \\
	\hline
	\end{tabular}
	\caption{The system built with 5 monomers per layer in a parallel displaced configuration results in a structure closest to experimental data~\label{fig:p2p} 
	\end{table}

@@

	Comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration
	\begin{itemize}
		\item Phase A
		\begin{itemize}	
			\item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
			\item There is evidence that the stacked configuration will shift towards an offset configuration over time. WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation 
			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
			\item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
		\end{itemize}
		\item Phase B
		\begin{itemize}
			\item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
			\item No spots at all which is consistent with the disorder shown by the rings in the pore
		\end{itemize}
		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\texsuperscript{-1} which is typical of packed alkane chains
		\item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B, they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present   
	\end{itemize}

@@

	Monomer configurations
	\begin{itemize}
		\item Pore-to-pore equilibration plots
                  %MRS: ^^^ probably should include how we determined if we ran long enough.
		\item 3D visualizations of different configurations tested
                  %MRS: vvv this might be in the main text, since it is what allows us to say what is more likely.
		\item Table of measurements on 5-8 monomer per layer configurations
		\item Sodium ion distribution in disordered phase
	\end{itemize}

        \includegraphics{placeholder.png}
                \caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
                \label{fig:initial}
        \end{figure}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{geometry}
\geometry{legalpaper, margin=1in}
\usepackage{amsmath} % or simply amstext
\newcommand{\angstrom}{\textup{\AA}}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Joseph Yelk \and Matthew Glaser \and Xunda Feng \and Michael R. Shirts} 
\begin{document}
	\bibliographystyle{ieeetr}
	\graphicspath{{./figures/}}
	\maketitle
	\section{Introduction}
	Nanostructured membrane materials have become increasingly popular for aqueous separations applications because they offer the ability to control membrane architecture at the atomic scale allowing design of solute-specific separation membranes.
	\begin{itemize}
		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
		\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
		\item Designing RO membranes to achieve targeted separations of specific solutes is nearly impossible due to the separation (hypothesized to be) controlled by fluctuating polymer voids
		\item RO has difficulty separating neutral organics because they tend to dissolve in polymer matrix
		\item Many current RO membranes degrade in typical chlorine filled municipal water supplies (debating this point because there aren't any studies of LLC membrane fouling resistance)
                %MRS: Doug should have information on the chemistry here and how resistant they might be.
		%BJC: Doug said they didn't do any chemical stability testing since the membranes had flux problems in the first place. So I won't mention this
		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
		\item Targeted separations can be accomplished by tuning the molecular building blocks which form these materials
		\item Entirely different mechanisms govern the separation processes in various nanostructured materials which can inspire novel separation techniques
	\end{itemize}

@@

	A molecular level understanding of LLC membrane structure will elucidate small molecule transport mechanisms, providing guidelines to reduce the chemical space for design of monomers used to create separation-specific membranes.
	\begin{itemize}
                \item We do not yet understand how to reduce the effective pore size and/or tune the chemical environment in the HII nanopores for effective water desalination and small organic separations. Rejection studies show that this membrane can not do desalination yet
%MRS: ^^^nice way to turn a weakness of the materials class into an opportunity to improve them requring research! 
		\item Colh phase studies currently limited to one monomer
                \item Optimization efforts performed through trial and error over the past 20 years
                \item Macroscopic models are the only source of predictive modeling and existing theories do not adequately describe transport at these length scales
                \begin{itemize}
                        \item What does the microscopic pore structure look like?
			\item Do ions have trouble getting through because of interactions with other things in the pores (e.g. ions, carbonyl groups, benzene rings) -- related to ionic conduction
			\item Is rejection of ions due to donnan exclusion?
                        \item Do neutral solutes get rejected based solely on size rejection, or do interactions within the pore lead to selective rejection?
                        \item Is water structured inside the pores, restricting low energy pathways for solutes to follow? %BJC: saw something like this in a paper
		\end{itemize}
		\item How can microscopic pore structure guide membrane design
		\item An atomistic understanding of the mechanism of solute transport can identify performance bottle necks and direct design of future monomers/membranes
		\item We can use molecular dynamics simulations to enhance our understanding 
	\end{itemize}

	A clear picture of the nanoscopic structure of LLC membranes, gained by building a molecular model, will provide evidence to support or call into question past drawn conclusions that have largely guided our understanding of separation mechanisms. 
	\begin{itemize}
		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
		\begin{itemize}
			\item This could change how one thinks about molecules diffusing through membrane
			\item Could also be a difference between lyotropic and thermotropic phases
		\end{itemize}
		\item The Colh phase is described as having pores made of disks or layers stacked on top of one another, each containing a set number of monomers. 
		\begin{itemize}
			\item How do the monomer head groups pack together? Do the benzene rings prefer to be stacked on top of each other or in another pi-stacking mode.
			\item Gas phase ab initio studies of benzene dimers have shown a clear energetic advantage for a parallel displaced or T-shaped conformation versus a stacked conformation. 
			\item Substituted benzene rings exhibit an even stronger pi-stacking attraction %BJC: reference ab initio papers   	
			\item A simple simulation study of a similar molecule (Head group is a sulfonate in the meta position) suggests that there are 4 monomers in each disk
			\item Calculations based on the volume of the liquid crystal suggest that there are seven monomers in each layer % reference 2005-ish Zhou paper 
		\end{itemize}
		\item It is possible there is more than one metastable states associated with this LLC system
		\begin{itemize}
			\item Which phase is consistent with experiment?
			\item Can both phases be created experimentally?
			\item How will each state affect transport?
		\end{itemize}
	\end{itemize}

	We must show that the developed molecular model is consistent with physical observations so that we can trust conclusions drawn about structural features characteristic of the system.
	\begin{itemize}
		\item This paper will illustrate the development of a predictive molecular model and the steps taken to ensure it mimics the real system as best we can 
		\item To understand how physically realistic the model is, validation by comparison to experiment is necessary
		\item We are primarily interested in reproducing the conclusions about structure which have been made from XRD experiments and ionic conductivity measurements.    
		\item We have comparied simulated X-ray diffraction patterns to experiment in order to match major features present in the 2D patterns
		\item We can predict ionic conductivity using two agreeing methods -- Collective diffusion and nernst einstein
		\item We examined crosslinking mechanism and understand its influence on membrane structure
	\end{itemize}

@@

	An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
	\begin{itemize}
		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
		\item Result not global minimum but close enough for structure building
		\item Antechamber used for atomtyping with gaff forcefield
		\item Used Openeye Quacpac molcharge.py to assign charges
		\item The am1bccsym method provided with Quacpac performs a conformational search and applies charges symmetrically based on the lowest energy subset of possible conformations
		\item Anneal again 
		\item Multiple configurations saved from annealing trajectory to prove independence of starting config. A representative structure is given in Figure ~\ref{fig:monatomistic}
		\item Manual modifications to the structure were made to create specific geometries for X-ray diffraction experiments
	\end{itemize}

	%BJC: I'm not sure where to place this figure. ACS nano requires the methods section to go last (after conclusions). It seems like this should go earlier, but it fits the context best around here.
	\begin{figure}
	\centering
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:chemdraw}
	\end{subfigure}
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:monatomistic}
	\end{subfigure}
	\medskip
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:cartoonlayer}
	\end{subfigure}
	\begin{subfigure}{.45\linewidth}
		\centering
		\includegraphics[width=\linewidth]{placeholder.png}
		\caption{}\label{fig:layeratomistic}
	\end{subfigure}
	\caption{(a) The chemical structure of NAGA3C11 (b) The chemical structure visualized atomistically enhances intuition about system behavior (c) Wedge-shaped monomers assemble into layers (d) An atomistic view of a layer suggests geometric constraints based on monomer structure}\label{fig:cartoonvatomistic}  
	\end{figure}

	The timescale for self assembly of monomers into the hexagonal phase is unknown and likely outside of a reasonable length for an atomistic simulation, calling for a more efficient way to build the system. 
	\begin{itemize}
		\item Work done shows coarse grain model self assembly in ~1000 ns , Citation: J. Phys. Chem. B 2013, 117, 4254-4262
		\item Attempts with Colh system not fruitful  
		\begin{itemize}
			\item Packed monomers into box with Packmol
			\item Simulated for ~100 ns with no progress shown towards self assembly
		\end{itemize}  
		\item Wrote code to assemble monomers into Colh configuration close to what is expected 
		\item Equilibration simulations allow structure to relax into expected configuration 
	\end{itemize}

@@

@@

	An equilibration scheme with position restraints placed on benzene rings prevents unrealistic jumps during early equilibration steps.
	\begin{itemize}
		\item Equilibration scheme:
		\begin{itemize}
			\item Apply position restraints to monomer head groups during energy minimization 
			\item Leave position restraints on for nvt simulations to allow tails to intermingle (this also helps ensure independence of starting monomer configuration)
			\item Gradually reduce force constants from 1000000 (by square root every 50 ps) until they are completely off
			\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate 
		\end{itemize}
	\end{itemize}

@@

	The Nernst Einstein relation and the Collective Diffusion model were both applied to the system in order to estimate ionic conductivity.
	\begin{itemize}
		\item There are a few ways to estimate ionic conductivity as seen in literature. We prefer a method which can extract an estimate based purely on an equilibrium trajectory (reference to computational electrophysiology) 
                \item We must also be sure that our analysis of results is consistent with the method used for experimental evaluation (i.e. AC impedance spectroscopy)
                \item We must also link our perfectly straight microscopic system to the not-so-straight macroscopic system. %BJC: worth getting into? Could also just say 
		% that we expect our calculated value to be higher since ours is perfectly aligned relative to the real system.
                \item Two methods used to for prediction
                \item Nernst Einstein Relation:
                \begin{itemize}
                        \item Widely used equation for estimating ionic conductivity
                        \item Estimates DC ionic conductivity -- Frequency used during AC impedance slow enough to be approximated by dc at short enough timescales
                        \item Relates the diffusive motion of ions in the membrane to the membrane's ionic conductivity
                        \item Concentration is concentration of ions in the whole membrane, not just channels
                \end{itemize}
                \item Collective Diffusion:  %BJC: will have a very topical explanation followed by a reference to the paper from which I got the method
                \begin{itemize}
                        \item Defines a collective coordinate, Q (charge), to quantify the amount of charge transfer through the system
                        \item In the limit of infinite time, the MSD of Q can be used to formulate a diffusion coefficient of Q that can be related to ionic conductivity
                        \item The model is valid for non-equilibrium and equilibrium simulations. Our analysis is based on the latter
                        \item A similar model has been derived and validate to predict water permeability using equilibrium simulations
                        \item The pore region is defined as the entire membrane system since lab IC measurements are done on bulk membrane rather than on individual pores. One would expect single channel IC to be much larger than the bulk membrane
                \end{itemize}
        \end{itemize}

@@

	To understand the composition of the monomer layers, we ran simulations created with 4 - 8 monomers per layer 
	\begin{itemize}
		\item All configurations were stable for at least a short time %BJC: I am going to run out these simulations further and will have more to say
                \item We showed that we can rule out systems consisting of 4, 7, and 8 monomers based purely on membrane dimensions (Table~\ref{table:p2p})
        \end{itemize}

	The initial distance between layers is a key determining factor of the equilibrium configuration.
	\begin{itemize}
                \item In the real system, layers are stacked 3.7 \angstrom apart based on WAXS data. 
                \item A characteristic of all systems simulated in this way, is a defined, cylindrical and open pore structure. Benzene rings arrange in a helical conformation after equil. Membrane about 8 nm thick (Fig ~\ref{fig:phaseA}) % BJC: Still trying to prove that layered is trying to go towards a helical conformation. Also, maybe include thickness in the table?
                \item This will be called phase A for simplicity  
	        \item Simulations of systems built with layers stacked 5 \angstrom apart results in a pore structure characterized by high radial disorder.
        	\begin{itemize}
                	\item This will be called phase B (Fig~\ref{fig:phaseB})
                	\item The arrangement of sodium ions (which are closely bound to carbonyl head groups) can be well-approximated by a gaussian distribution 
                	\item Like phase A, phase B can form at 280K. The only difference in simulations leading to this state, is the initial interlayer spacing
                	\item The phase is also present when phase A is heated close to its isotropic transition point
                	\item There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})
                	\begin{itemize}
                        	\item Phase B has a closed pore, while phase A is open. This will impact transport mechanisms
                        	\item Phase B membranes are thicker
                        	\item Consequently, the pore spacing is smaller
                	\end{itemize}
		\end{itemize}
                \item We have at least two metastable states
        \end{itemize}

	We varied the relative interlayer orientation between sandwiched and parallel-displaced based on our knowledge of the stability of these two pi-stacking modes.
        \begin{itemize}
		\item Simulated Xray diffraction patterns generated from initial configurations of each pi-stacking mode, shows a clear relation between the parallel displaced configuration and major features present in the XRD patterns %BJC: A figure would probably be good here
		\item Diagonal spots in the alkane chain region are only generated for structures created in the parallel displaced configuration
		\item However, both configurations are stable for 100's of nanoseconds
		\item Xray diffraction of the sandwiched configuration after equilibration shows the spots. This indicates that there is a shift towards the offset configuration.
	\end{itemize}

@@

	A summary of all experiments and relevant structural parameters are presented in table ~\ref{table:p2p}

	\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{placeholder.png}
	\caption{As temperature is increased, Phase A transitions to Phase B, as indicated by the shown order parameter. An order parameter of 1 indicates perfect ordering, while 0 indicates disorder}\label{fig:transition}
	\end{figure}

	\begin{table}
	\centering
	\begin{tabular}{|c|c|}
	\hline
	table & here \\
	\hline
	\end{tabular}
	\caption{A system built with 5 monomers per layer in a parallel displaced configuration results in a structure closest to experimental data}\label{table:p2p} 
	\end{table}

@@

	%BJC: I might eliminate the other paragraph (2 before this one), where I justify parallel-displaced vs. sandwiched, and do it all in this paragraph.	
	Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
	\begin{itemize}
		\item Phase A
		\begin{itemize}	
			\item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
			\item There is evidence that the stacked configuration will shift towards an offset configuration over time. WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation 
			\item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
			\item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
		\end{itemize}
		\item Phase B
		\begin{itemize}
			\item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
			\item No spots at all which is consistent with the disorder shown by the rings in the pore
		\end{itemize}
		\item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom\textsuperscript{-1} which is typical of packed alkane chains
		\item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B, they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present   
	\end{itemize}

@@

	Monomer configurations
	\begin{itemize}
		\item Pore-to-pore equilibration plots
		\item Plots of other things that level off indicating equilibration
		\item 3D visualizations of different configurations tested
		\item Sodium ion distribution in disordered phase
	\end{itemize}

        \begin{figure}
		\centering
		\includegraphics{placeholder.png}
                \caption{Monomers are placed in an initial configuration close to the expected equilibrium configuration and allowed to relax}
                \label{fig:initial}
        \end{figure}
